\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathabx}
\usepackage{mathpazo}
\usepackage[mmddyy]{datetime}
\usepackage{hyperref}

\usetheme{Dresden}
\usefonttheme{serif}
\usecolortheme{rose}


\title{OSDEV-102: Environment Setup}
\author{Levente Kurusa}
\institute{lkurusa@acm.org}
\date{Last modified: \today}

\begin{document}
\maketitle

\begin{frame}{Requirements}
  \begin{itemize}
		\item Preferrably a Linux system
		\item gcc
		\item nasm x86-32 assembler
		\item a text editor of your choice
  \end{itemize}
\end{frame}

\begin{frame}{Getting the tools}
  \begin{itemize}
		\item \texttt{\# apt-get install gcc make git qemu}
		\item \texttt{\# dnf install gcc make git qemu-system-i386}
  \end{itemize}
  We need \texttt{gcc} for compiling stuff, \texttt{make} for making that easy,
  \texttt{git} for souce code control and \texttt{qemu} to avoid damaging your own
  computer.
\end{frame}

\begin{frame}{git}
  If you are not familiar with git, please refer to this website: \\
  http://try.github.io/
\end{frame}

\begin{frame}{Repository}
  The course has a central repository where all checkpoints have the code in case you
  get stuck.
  \begin{itemize}
          \item https://github.com/levex/osdev-course
  \end{itemize}
  Please clone this repository. If you have successfully cloned it, that means your git
  is working!
\end{frame}

\begin{frame}{nasm and qemu}
  \texttt{nasm} is our i386 assembler (more on this later) of our choice. \\
  In the repo, you will find \texttt{tests/nasm/01.S}. Run the following commands: \\
  \texttt{\$ nasm tests/nasm/01.S -o test\_out.img} \\
  \texttt{\$ qemu-system-i386 -fda test\_out.img} \\
  If you see a screen popup full black, with a text saying "It worked", then you are
  good to go!
\end{frame}

\begin{frame}{Troubleshooting}
  \begin{itemize}
		\item Check whether \texttt{nasm}, \texttt{git} can be run by themselves.
		\item If yes, you are most likely missing the repository or are in the wrong working directory.
		\item Otherwise you need to reinstall them using your package manager.
  \end{itemize}
\end{frame}
\end{document}
